Extracting data for time slice analyses

### 2017-11-29 analyses/01-extract-data-for-analyses.Rmd
Add trimming to matrix to remove taxa that do not overlap

@@

>>>>

One final issue is that to commute Gower distances we need all taxa to have some overlapping data. If not Gower distances will be NA (Gower distance does not impute missing data like some other methods). To avoid this problem we can remove the taxa with no overlaps as follows. This is commented out below because there are no non overlapping taxa in the Beck and Lee 2014 dataset.

```{r}
## Trimming the distance matrix
## trim <- TrimMorphDistMatrix(matrix_dist)
## matrix_dist <- trim$dist.matrix

## Which taxa were removed?
## as.vector(trim$removed.taxa)

## Rewrite this to file for later use
## saveRDS(matrix_dist, file = paste0("../data/processed/distance_matrix.", slug ,".Rda"))
```

@@

## Constructing the distance matrix
matrix_dist <- MorphDistMatrixFast(matrix, distance = "Gower")

## Trim taxa with non overlapping data
trim <- TrimMorphDistMatrix(matrix_dist)
matrix_dist <- trim$dist.matrix

## Which taxa were removed?
as.vector(trim$removed.taxa)

## Save
saveRDS(matrix_dist, file = paste0("../data/processed/distance_matrix.", slug ,".Rda"))
```
